Computing Entropies With Nested Sampling

### 2017-07-11 paper/ms.tex
NS parameters

In the following sections I demonstrate the algorithm on three
example problems.

@@

Throughout this paper, the question of how to sample from the constrained
distributions required by NS has not been discussed in detail. For the examples,
I used the original \citet{skilling} suggestion of using a short MCMC run
initialised at a surviving point. In some problems, this will not be effective,
and this will cause the resulting estimates to be incorrect, as in standard
Nested Sampling applications. Despite this, the algorithm should still be
useful in a wide range of applications.

>>>>

In the following sections I demonstrate the algorithm on three
example problems. For each of the examples, I did 1000 repetitions of NS
(i.e., 1000 reference particles), and used 10 NS particles and 10000 MCMC
steps per NS iteration.

@@

Throughout this paper, the question of how to sample from the constrained
distributions required by NS has not been discussed in detail. For the examples,
I used the original \citet{skilling2006nested} suggestion of using a short MCMC run
initialised at a surviving point. In some problems, this will not be effective,
and this will cause the resulting estimates to be incorrect, as in standard
Nested Sampling applications. Despite this, the algorithm should still be
useful in a wide range of applications.
